Ornaments as indicators of Social change before and after European contact at Kiwulan, Northeastern Taiwan

### 2019-08-14 analysis/paper/paper.Rmd
make plot titles consistent

ornaments_period_join_cen <- 
  ornaments_period_join_cen_all %>% 
  group_by(period) %>% 
  group_split() %>% 
  set_names(c("Pre-European",
              "European",
              "Chinese"))
```

>>>>

ornaments_period_join_cen <- 
  ornaments_period_join_cen_all %>% 
  group_by(period) %>% 
  group_split() %>% 
  set_names(c("Before European Contact",
              "European Contact",
              "Chinese Contact"))
```
